---
title: "Social Network Analysis <br/> Home Assignment 2"
author: '{rashid ali}'
date: "due date - 29.05.2017 23:59"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---
# Graph models. Centrality metrics
Please send your reports to hse.ntwks@gmail.com with the subject of of the following structure:<br/>
*[MAGOLEGO SNA 2017] {ali} {rashid} HA{2}*

Late submission policy: -1 point per day

Use this file as a template for your report.\
Support your computations with figures and comments. Send ONLY .Rmd versions of your report with datasets for your social network. Anonymize your data if necessary.

```{r, echo=FALSE}
library(igraph)
library(rgexf)
library(ggplot2)
library(R.matlab)
library(xtable)
```


## Task 1. Your social network

For the first task, you have to load your [vk.com](http://vk.com) network. Please follow the instructions posted on the course wiki or user [VK Application](vk.com/app3861133). For [FB](http://facebook.com) users try to use [NetVizz](http://thepoliticsofsystems.net/2010/03/netvizz-facebook-to-gephi/). If you did it correctly, you should have a GraphML file with your own network. Read it to R:

```{r}
## Put your code here
vknet = read.gexf("vk-friends-2.gexf")
vkfg <- gexf.to.igraph(vknet)
#Hide origional names of vertices 
gvc <- vcount(vkfg)
gec <- ecount(vkfg)
vkfg_adj_mat <- get.adjacency(vkfg)
vkfg_adj_mat_names <- 1:gvc
colnames(vkfg_adj_mat) <- vkfg_adj_mat_names
row.names(vkfg_adj_mat) <- colnames(vkfg_adj_mat)
vkfg <- graph.adjacency(vkfg_adj_mat, add.colnames = "T")


```

### 1. Degree distribution

First, plot degree distribution of your network in log-log scales:

```{r}
## Put your code here
vkfg_degree <- degree(vkfg)
vkfg_degree <- vkfg_degree+1
dmax <- max(vkfg_degree)
dmin <- min(vkfg_degree)
drange <- as.numeric(dmin:dmax)
degree_dist <- degree.distribution(vkfg)[drange]

pl_fit <- power.law.fit(vkfg_degree, xmin = NULL, implementation = "plfit")
alpha <- pl_fit$alpha
xmin <- pl_fit$xmin
C <- (alpha-1)* xmin^(alpha-1)
pldf <- function(x) return(C*x^(-alpha))
plot(degree_dist, log = 'xy', main = "VK friends graph distribution", xlab = " node degree log", ylab = " Degree distribution log" )
par(new = T)
curve(pldf, from = dmin, to = dmax, log="xy", main = "", xlab = "", ylab = "", col = "red", axes = F, add = F)



```

Is there any correspondence between actual degree distribution of your network and the Power Law distribution? If not, explain why.

*Put your comments here*

Now, let's see how it would look if it was random. Produce Erdos-Renyi graph matching your real network (same number of nodes and same average degree). Compare it with your degree distribution.

```{r}
## Put your code here

er_graph <- erdos.renyi.game(gvc, gec, type = "gnm")

degree_dist_erg <- degree.distribution(er_graph)
plot(degree_dist, log = "xy", main = " VK friend graph Vs Erdos-renyi graph", xlab = "Node Degree log", ylab = " Degree distribution log")
par(new = T)
plot(degree_dist_erg, log = "xy" ,main =" ", col= "red", axes = F)

```

*according to ks test, the pl_fit$ks.p= 0.9670 which is greater than 0.05, so there is good correspondece  between actual degree distribution and power law distrubution*

### 2. Compute centrality metrics

Compute for your network: 

* degree centrality

* closeness centrality

* betweenness centrality

* eigenvector centrality

* Bonacich power centrality

* Alpha centrality


```{r}
## Put your code here
degcen <- centralization.degree(vkfg)

closecen <- centralization.closeness(vkfg, mode="all")

betcen <- centralization.betweenness (vkfg, directed = TRUE, nobigint = TRUE)

ev_cen <- centralization.evcent (vkfg, directed = TRUE, scale = FALSE, options = igraph.arpack.default)


degcen$centralization
closecen$centralization
betcen$centralization
ev_cen$centralization



```

Output six plots corresponding to six centrality metrics you've computed: 

* Use first names of your friends as node labels on the graph (you may hide this information if you wish -- change it by integer ID)
* Keep the same layout of the network
* Make node sizes and colours proportional to the respective centrality metrics

Hint: If you get stuck, lab 4 script might be helpful.

```{r fig.width = 10, fig.height = 10 }
## Put your code here
deg<-degree(vkfg)
lay <- layout.fruchterman.reingold(vkfg)
fine = 500
palette2 <- colorRampPalette(c('blue','red'))
degCol <- palette2(fine)[as.numeric(cut(deg,breaks = fine))]
vert_size <- ifelse(deg>30, 1/30*deg, 1)
par(mfrow=c(1,1))
plot(vkfg, layout=lay, vertex.color=degCol, vertex.size=vert_size*5, vertex.label=NA, edge.width = 0.5, edge.arrow.size = 0.5, main="Degree centrality")


```

```{r}
clos <- closeness(vkfg)
closCol = palette2(fine)[as.numeric(cut(clos,breaks = fine))]
plot(vkfg,layout = lay, vertex.label=NA, vertex.color=closCol, vertex.size=clos*23000, edge.width = 0.5, edge.arrow.size = 0.5, main="Closeness centrality")

```

```{r}
betw <- betweenness(vkfg)
betwCol = palette2(fine)[as.numeric(cut(betw,breaks = fine))]
vert_size <- ifelse(betw>210, 1/210*betw, 1)
plot(vkfg,layout = lay, vertex.color=betwCol, vertex.size=vert_size*15, vertex.label=NA, edge.width = 0.5, edge.arrow.size = 0.5, main="Betwenness centrality")

```

```{r}
ev <- evcent(vkfg)$vector
evCol = palette2(fine)[as.numeric(cut(ev,breaks = fine))]
vert_size <- ifelse(ev>0.15, 5*ev, 0.8)
plot(vkfg,layout = lay, vertex.size=vert_size*10, vertex.color=evCol, vertex.label=NA, edge.width = 0.5, edge.arrow.size = 0.5, main="Eigenvector centrality")


```



```{r}
# I got some errors while calculating alpha and bonacich centrality when using vk-friends.gexf-2. So, I tired a new social graph for alpha and bonacich centrality 
vknet2 = read.gexf("vk-friends.gexf")
vkfg2 <- gexf.to.igraph(vknet2)
#Hide origional names of vertices 
gvc2 <- vcount(vkfg2)
gec2 <- ecount(vkfg2)
vkfg_adj_mat2 <- get.adjacency(vkfg2)
vkfg_adj_mat_names2 <- 1:gvc2
colnames(vkfg_adj_mat2) <- vkfg_adj_mat_names2
row.names(vkfg_adj_mat2) <- colnames(vkfg_adj_mat2)
vkfg2 <- graph.adjacency(vkfg_adj_mat2, add.colnames = "T")

```




```{r}

bon_cen <- bonpow(vkfg2)

evCol = palette2(fine)[as.numeric(cut(bon_cen,breaks = fine))]
vert_size <- ifelse(bon_cen>0.15, 5*ev, 0.8)
plot(vkfg,layout = lay, vertex.size=vert_size*10, vertex.color=evCol, vertex.label=NA, edge.width = 0.5, edge.arrow.size = 0.5, main="Bonacich power centrality")

```


```{r}
alpha_cen <- alpha.centrality(vkfg2)

evCol = palette2(fine)[as.numeric(cut(alpha_cen,breaks = fine))]
vert_size <- ifelse(alpha_cen>0.15, 5*ev, 0.8)
plot(vkfg,layout = lay, vertex.size=vert_size*10, vertex.color=evCol, vertex.label=NA, edge.width = 0.5, edge.arrow.size = 0.5,
     main=" alpha centrality")


```

Now, output top ten nodes in each ranking. Again, print only first names in your table to keep privacy:



```{r}

deg_cent_top10 <-sort(deg, decreasing = TRUE)[1:10]
deg_cent_top10.mat = cbind(vkfg$v[deg_cent_top10] , deg_cent_top10)
#colnames(g.deg.cent.top10.mat) = c("Node", "Degree Centrality")
print(deg_cent_top10.mat)

clos_cent_top10 <- sort(clos, decreasing = TRUE)[1:10]
clos_cent_top10.mat = cbind(vkfg$v[clos_cent_top10] , clos_cent_top10)
print(clos_cent_top10.mat)

betcent<-sort(betw, decreasing = TRUE)[1:10]
bet_cent_top10.mat = cbind(vkfg$v[betcent] , betcent)
print(bet_cent_top10.mat)

evcent <- sort(ev, decreasing = TRUE)[1:10]
ev_cent_top10.mat = cbind(vkfg$v[evcent] , evcent)
print(ev_cent_top10.mat)

boncent<-sort(bon_cen, decreasing = TRUE)[1:10]
boncent_top10.mat = cbind(vkfg$v[boncent] , boncent)
print(boncent_top10.mat)

alcent<-sort(alpha_cen, decreasing = TRUE)[1:10]
al_cent_top10.mat = cbind(vkfg$v[alcent] , alcent)
print(al_cent_top10.mat)
```



*Comment on your results here - for example, why some nodes have high betweenness centrality and the others have high closeness centrality. Is this what you would expect to see?*
*Highest between is centrality is 14 which is expected because the red node in between centrality is a link between nodes on both sides but the values of closeness centrality is realitvely low* 


## Task 2. Flickr network

In the second task, you will work with a large directed graph. 

Please download [flickr.mat](http://www.hse.ru/data/2015/05/01/1098247366/flickr.mat) 

*Data contains sparse matrix A and list of user names. This is a denser part of the Flickr photo sharing site friendship graph from 2006. Edge direction corresponds to friendship requests (following). Some of the links are reciprocal, others not*

It's a Matlab file. How to deal with it in R? There is a package `R.matlab`. Please install it and call `library(R.matlab)`

Now use `readMat` function to read the file and extract adjacency matrix and a list of user names:

```{r, eval=FALSE}
flickr = readMat("flickr.mat")
fmatrix=as.matrix(flickr[1]$A)
fnames=flickr[2]$names
```

If you have trouble loading large mat file on your laptop --- try to use HSE computer classes with installed R+RStudio.

Look at user names. You might want to remove spaces from the names. Use a function `gsub` to remove them:

```{r, eval=FALSE}
fnames=gsub(" ", "", fnames)
```

Now create a graph, output the number of vertices and edges:

```{r}
## Put your code here

flicker_net<- graph.adjacency(fmatrix, mode = "directed", weighted = NULL)
vcount(flicker_net)
ecount(flicker_net)


```

Compute in- and out- degree centralities, PageRank, Hubs and Authorities for this network:

```{r}
## Put your code here

deg_cen_i <-centralization.degree(flicker_net, mode = "in")$centralization
#deg_cen_i
deg_cen_o <-centralization.degree(flicker_net, mode = "out")$centralization
#deg_cen_o
flicker_pr <- page.rank(flicker_net)$vector
#flicker_pr
flicker_hub <- hub.score(flicker_net)$vector
#flicker_hub
flicker_auth <- authority.score(flicker_net)$vector




```

Print top ten names in each ranking:

```{r}
## Put your code here

deg_in<-degree(flicker_net, mode = "in")
top_in <- sort(deg_in, decreasing = TRUE)[1:10]
fnames[which(deg_in %in% top_in)]

deg_out=degree(flicker_net, mode = "out")
top_out <- sort(deg_out, decreasing = TRUE)[1:10]
fnames[which(deg_out %in% top_out)]

top_pr <- sort(flicker_pr, decreasing = TRUE)[1:10]
fnames[which(flicker_pr %in% top_pr)]

top_hub <- sort(flicker_hub, decreasing = TRUE)[1:10]
fnames[which(flicker_hub %in% top_hub)]

top_auth <- sort(flicker_auth, decreasing = TRUE)[1:10]
fnames[which(flicker_auth %in% top_auth)]



```

Produce the following plots:

* In-degree centralities versus out-degree centralities

* In-degree centralities versus authorities

* Out-degree centralities versus hubs

* Hubs versus authorities

* PageRank versus hubs

* PageRank versus authorities


```{r}
## Put your code here

par(mfrow = c(3, 2)) 
plot(deg_in, deg_out, col="green", xlab = "In degree", ylab = "Out degree")
plot(deg_in, flicker_auth, col="green", xlab = "In degree", ylab = "Authority")
plot(deg_out, flicker_hub, col="green", xlab = "Out degree", ylab = "Hubs")
plot(flicker_hub, flicker_auth, col="green", xlab = "Hubs", ylab = "Authority")
plot(flicker_pr, flicker_hub, col="green", xlab = "Page Rank", ylab = "Hubs")
plot(flicker_pr, flicker_auth, col="green", xlab = "Page Rank", ylab = "Authority")


```

*For <in-degree, authority>, <out-degree, hub> and <pagerank, authority> pairs a positive correlation is revealed, as opposed to the rest of those being compared *
