---
title: "Social Network Analysis <br/> Home Assignment 3"
author: '{rashid ali}'
date: "due date - 05.06.2017 23:59"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---
# Network communities
Please send your reports to hse.ntwks@gmail.com with the subject of of the following structure:<br/>
*[MAGOLEGO SNA 2017] {ali} {rashid} HW{3}*

Late submission policy: -1 point per day

Use this file as a template for your report.\
Support your computations with figures and comments. Send ONLY .Rmd versions of your report.

```{r, echo=FALSE}
library(igraph)
```


## Yahoo Music Network

For this assignment, you have to load [the part of Yahoo Music Network](https://drive.google.com/file/d/0Bwd5a7NScgMtNElfOFdSbE1UYnM/view). Archive contains network in GML format and corresponding list of artists.

```{r}
## Put your code here

yahoo_music_net <- read.graph("music2K.gml", format = "gml" )

artists_names <- scan("artists.txt", what="", sep="\n")
V(yahoo_music_net)$label = artists_names
```

Edges in this network appear if enough number of users have given ratings to both music bands. Note, that edges are weighted with similarity of the ratings.


### 1. Preprocessing

This network needs to be preprocessed. Do the steps, described on seminar, to make it look properly. How many vertices and edges were deleted?

```{r}
## Put your code here
v1 <- vcount(yahoo_music_net)
e1 <- ecount(yahoo_music_net)
yahoo_music_net <- delete.vertices(yahoo_music_net, degree(yahoo_music_net) == 0)
yahoo_music_net <- simplify(yahoo_music_net)
v2 <- vcount(yahoo_music_net)
e2 <- ecount(yahoo_music_net)

v1 - v2
e1 - e2
```
# 4 vertices and 0 edges are deleted

### 2. Clustering

Define clusters for this networks using one of the algorithms described on lectures and seminars:
```{r}
## Put your code here
mc <- multilevel.community(yahoo_music_net,weights = NULL )
```

Compute density of obtained clusters:
```{r}
## Put your code here

density_clusters <- 1: length(mc)
inner_con <- 1:length(mc)

for (j in 1: length(mc)){
  subg <- induced.subgraph(yahoo_music_net, which(mc$membership==j))
 inner_con[j] <- ecount(subg)
 density_clusters[j] <- graph.density(yahoo_music_net)
}
density_clusters
```

Compute the ratio of inner clusters connections to outer ones:
```{r}
## Put your code here

sum(inner_con)/ecount(yahoo_music_net)

```


### 3. Visualization & interpretation

Visulize five of the most dense clusters. Use names of artists as node labels on the graph.
```{r}
## Put your code here
index_max1 <- which.max(density_clusters)
density_clusters[index_max1] <- 0
index_max2 <- which.max(density_clusters)
density_clusters[index_max2] <- 0
index_max3 <- which.max(density_clusters)
density_clusters[index_max3] <- 0
index_max4 <- which.max(density_clusters)
density_clusters[index_max4] <- 0
index_max5 <- which.max(density_clusters)

subgraph1 <- induced.subgraph(yahoo_music_net,which(mc$membership == index_max1))

plot(subgraph1, layout= layout.circle )

```

```{r}
subgraph2 <- induced.subgraph(yahoo_music_net,which(mc$membership == index_max2))
plot(subgraph2, layout=layout.circle)
```

```{r}
subgraph3 <- induced.subgraph(yahoo_music_net,which(mc$membership == index_max3))
plot(subgraph3, layout=lay)
```
```{r}
subgraph4 <- induced.subgraph(yahoo_music_net,which(mc$membership == index_max4))
plot(subgraph4, layout=layout.circle)
```

```{r}
subgraph5 <- induced.subgraph(yahoo_music_net,which(mc$membership == index_max5))
plot(subgraph5, layout=layout.circle)
```

<b> (Extra task) </b>Try to interpret (using Wikipedia or other resources) obtained clusters.

*THe clusters show the different type of music grouped in different clusters*