---
title: "Social Network Analysis <br/> Home Assignment 4"
author: '{rashid ali}'
date: "due date - 12.06.2016 23:59"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---
# Network Epidemics

Please send your reports to hse.ntwks@gmail.com with the subject of of the following structure:<br/>
*[MAGOLEGO SNA 2017] {ali} {rashid} HW{4}*

Late submission policy: -2 points per day

Use this file as a template for your report.\
Support your computations with figures and comments. Send ONLY .Rmd versions of your report.

```{r, echo=FALSE}
library(igraph)
library(EpiModel)
```
## SIR Model

You need to perform epidemic SIR model on different types of networks:
Try different parameters for network generation
```{r}
gl <- list()
gl$ba <- barabasi.game(n = 100,m = 12 , directed=FALSE)
gl$er <- erdos.renyi.game(n = 250, p.or.m = 0.02, type=c("gnp"))
gl$ws <- watts.strogatz.game(dim = 1, size = 1000, nei = 3, p = 0.01)
``` 

Moreover perform modeling on real peer-to-peer network [here](https://www.hse.ru/data/2016/04/21/1130159900/Net.txt)
```{r}
real_net <- read.table("Net.txt")
real_net <- t(as.matrix(real_net))
real_net <-real_net+1
g<- graph(real_net)
gl$real_net <- g

```


Your goal is to perform a research on epidemics:
Use different values of parameters listed below
```{r}
beta <- 2
gamma <- 4
ntrials <- 100

# Running function sir for each element of list gl (list with graphs)
sim <- lapply(gl, sir, beta=beta, gamma=gamma, no.sim=ntrials)
```
at least 3 different versions, for example:

* betta (4 6 8)
* gamma (8 6 2)
* niter (100 500 1000)
    
*For some reason `beta` and `gamma` parameters should not be set below 0 and 1. Looks like they are somehow normilized during simulation.*

You need to plot three values on the graphics: Number of infected, number of suseprible, number of recovered - all depends on time.
As a result of this task, you need to provide 12 plots (one for each network with 3 diferent parameters) with explanation.
```{r}
plot(sim$er)
```

```{r}
plot(sim$ba, color="palegoldenrod", median_color="gold", quantile_color="gold")
```

```{r}
plot(sim$ws, color="pink", median_color="red", quantile_color="red")
```
```{r}
plot(sim$real_net)
```

```{r}
x.max <- max(sapply(sapply(sim, time_bins), max))
y.max <- 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NI"]]), max, na.rm=TRUE))

plot(time_bins(sim$er), median(sim$er)[["NI"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[I](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NI"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NI"]],lwd=2, col="red")
lines(time_bins(sim$real_net), median(sim$real_net)[["NI"]], lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)
```
*Comment: The infection rate for real net is high in start but it decreases with time and the infection rate for rate for Er,ba and ws is almost constant*




```{r}
beta <- 4
gamma <- 8
ntrials <- 100

# Running function sir for each element of list gl (list with graphs)
sim <- lapply(gl, sir, beta=beta, gamma=gamma, no.sim=ntrials)
```

```{r}

plot(sim$er)
```

```{r}
plot(sim$ba, color="palegoldenrod", median_color="gold", quantile_color="gold")
```
```{r}
plot(sim$ws, color="pink", median_color="red", quantile_color="red")

```

```{r}
plot(sim$real_net, color = "green")
```

```{r}
x.max <- max(sapply(sapply(sim, time_bins), max))
y.max <- 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NI"]]), max, na.rm=TRUE))

plot(time_bins(sim$er), median(sim$er)[["NI"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[I](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NI"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NI"]],lwd=2, col="red")
lines(time_bins(sim$real_net), median(sim$real_net)[["NI"]], lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)
```
*Comment: The infection rate for real net is high in start but it decreases with time and the infection rate for rate for Er,ba and ws is almost constant*

```{r}
beta <- 2
gamma <- 9
ntrials <- 500

# Running function sir for each element of list gl (list with graphs)
sim <- lapply(gl, sir, beta=beta, gamma=gamma, no.sim=ntrials)
```

```{r}
plot(sim$er)
```

```{r}
plot(sim$ba, color="palegoldenrod", median_color="gold", quantile_color="gold")
```

```{r}
plot(sim$ws, color="pink", median_color="red", quantile_color="red")
```

```{r}
plot(sim$real_net, color = "green")
```

```{r}
x.max <- max(sapply(sapply(sim, time_bins), max))
y.max <- 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NI"]]), max, na.rm=TRUE))

plot(time_bins(sim$er), median(sim$er)[["NI"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[I](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NI"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NI"]],lwd=2, col="red")
lines(time_bins(sim$real_net), median(sim$real_net)[["NI"]], lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)
```
*Comment: The infection rate for real net is high in start but it abruptly decreases with time and the infection rate for rate for Er,ba and ws is almost constant and abrupt decrease is due to high difference between beta and gamma*

```{r}
beta <- 8
gamma <- 2
ntrials <- 1000

# Running function sir for each element of list gl (list with graphs)
sim <- lapply(gl, sir, beta=beta, gamma=gamma, no.sim=ntrials)
```

```{r}
plot(sim$er)
```

```{r}
plot(sim$ba, color="palegoldenrod", median_color="gold", quantile_color="gold")
```

```{r}
plot(sim$ws, color="pink", median_color="red", quantile_color="red")
```


```{r}
plot(sim$real_net, color = "green")
```

```{r}
x.max <- max(sapply(sapply(sim, time_bins), max))
y.max <- 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NI"]]), max, na.rm=TRUE))

plot(time_bins(sim$er), median(sim$er)[["NI"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[I](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NI"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NI"]],lwd=2, col="red")
lines(time_bins(sim$real_net), median(sim$real_net)[["NI"]], lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)
```

*Comment: The infection rate for real net is high in start but it decreases with time and the infection rate for rate for Er,ba and ws is almost constant*

